---
title: "Laptop Market Analysis"
author: "Nur Shasha"
date: "2026-02-24"
output: github_document
---
## Data Cleaning and Factor Construction
We use the Laptop Data from Kaggle. First, we remove empty rows and convert the `TypeName` column into **Factors** to categorize laptops correctly.

```{r setup_data}
# Load and clean data
laptops <- read.csv("laptopData.csv")
laptops <- na.omit(laptops)

# Create Factor for Laptop Types
laptops$TypeName <- factor(laptops$TypeName)

# Display table of counts
table(laptops$TypeName)
```

## Visualization and Selection Logic (Lab 5)
In this section, we visualize the price distribution and use a selection statement to provide market insights.

```{r analysis}
# This code MUST be inside these three backticks to run!
hist(laptops$Price, 
     main="Laptop Price Distribution", 
     xlab="Price (INR)", 
     col="lightblue", 
     border="white")

# Selection Logic (Lab 5)
avg_price <- mean(laptops$Price)

if (avg_price > 60000) {
  print(paste("Insight: Market average is premium:", round(avg_price, 2)))
} else {
  print(paste("Insight: Market average is budget-friendly:", round(avg_price, 2)))
}
```
## References
* **Dataset:** Laptop Price Dataset, Kaggle. [https://www.kaggle.com/datasets/ehtishamsadiq/uncleaned-laptop-price-dataset/data](https://www.kaggle.com/datasets/ehtishamsadiq/uncleaned-laptop-price-dataset/data)
* **Course Material:** TEB2043 Data Science, Universiti Teknologi PETRONAS (UTP)